---
title: "TemparatuR API vignette"
author: "Carolina Rosário and Elisio Quintino"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TemparatuR_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>" 
)
```


## Setup
```{r setup}
library(temperatuR)
```

## Usage 

 
### Get temperatuR information for every station using getInfoStations

Here is how we can get information about every station and it's latitude (lat), longitude (lon), municipality of the measuring point (kommun), county of the measuring point (lan) and meter above Sea Level(moh). 
Since temperatuR API has more than 1500 stations, we will use the function head that will return, by default, the first 6 rows.

```{r}
agent = temperaturNuAgent()
info_stations = agent$getInfoStations()
head(info_stations)
```


### Get temperatureR information for a specific station using getTForStation

Now, here is how we can get information for a specific station and it's measured temperature in degrees celsius by date and time. In this function, since we want to access temperature of a specific station in a specific timeline, we have to use as input values for our function, a station, a start date and an end date.

As an example, let's use the first shown city in the previous case **aareavaara**, and some randomly selected dates like,  **"2021-06-06-21-00"** and **"2021-06-07-21-00"**.

```{r}
info_stations_aareavaara = agent$getTForStation("aareavaara","2021-06-06-21-00","2021-06-07-21-00")
print(info_stations_aareavaara)

```




